---
title: "R Notebook"
output: html_notebook
---
Let's see what we need to do.
1. Form a window containing 500 tickers for each quarter.
(To save memory, we can use a function to decide in a certain quarter, 
what's the stock list for SP500.)
2. Manage the IBES forecast feature.
3. Manage CRSP feature and do calculation.
3. Store them and prepare for regression.

```{r,,warning=FALSE}
# options(warn=-1)
library(writexl)
library(readxl)
library(dplyr)
library(reshape2)
library(ggcorrplot)
library(ggplot2)
library(scales)
library(aTSA)
library(pracma)
library(rstan)
```

Import datasets.

```{r,warning=FALSE}
date_range <- readxl::read_excel("D:\\data\\Capstone\\Data\\Valid_date_range.xlsx")
date_range$thru[is.na(date_range$thru)] <- 20190101

crsp <- readxl::read_excel("D:\\data\\Capstone\\Data\\CRSP_Features.xlsx")

# Final Subset to screen the stocks with 5 selected features.
crsp_f <- subset(crsp, select = c(gvkey, date, mv, dvy, e2pfy0, b2p, s2ev))

ohlc <- readxl::read_excel("D:\\data\\Capstone\\Data\\OHLC_quarter.xlsx")
link_key <- readxl::read_excel("D:\\data\\Capstone\\Data\\LK.xlsx")

tech_factors <- readxl::read_excel("D:\\data\\Capstone\\Data\\Tech_Factors.xlsx")
```

Support Functions.
```{r}
# This function would return the consititute of SP500 with gvkey, ticker and cusip
# during given start date and end date.
get_SPlist <- function(start_date, end_date) {
  temp <- subset(date_range, (date_range$from <= start_date) & (date_range$thru >= end_date),
    select = c(gvkey, co_tic, co_cusip)
  )
  temp
}
#### Test function.
# test = get_SPlist(19950101,19950331)

# This function would be used to transform year,quarter to yyyymmdd format.
trans_YQ_to_date <- function(year, qtr) {
  year * 10000 + qtr * 3 * 100 + 31
}

# This function would determine the lookback period for a certain quarter.
get_lkbk_period <- function(year, qtr) {
  if (qtr == 1) {
    c(year - 6, 4, year - 1, 4)
  } else {
    c(year - 5, qtr - 1, year, qtr - 1)
  }
}

# This function would determine the lookback period for a certain quarter(tech ver.).
get_lkbk_period_tech <- function(year, qtr) {
  if (qtr == 1) {
    c(year - 1, 4)
  } else {
    c(year, qtr - 1)
  }
}

# Provide corresponding keys from key given.
trans_gvk_to_permno <- function(gvkeys, LK) {
  NList <- subset(LK, (LK$gvkey %in% gvkeys), select = c(gvkey, permno))
  NList
}
#### Test function.
# test1 = pull(link_key[sample(nrow(link_key[,1]), 10, replace=F),1])
# test2 = trans_gvk_to_permno(test1,link_key)

# Do linear regression and prediction of the return in next quarter.
reg_pred <- function(df) {
  x <- df[1:20, ]
  x <- x[complete.cases(x), ]
  y <- df[21, ]
  y <- y[complete.cases(y), ]
  pred <- data.frame(matrix(ncol = 3, nrow = 0))
  names(pred) <- c("gvkey", "pred", "actual")
  if ((nrow(x) > 5) & (nrow(y))) {
    ols.fit <- lm(formula = ret ~ mv + dvy + e2pfy0 + b2p + s2ev, data = x)
    pred[1, ] <- c(y$gvkey, predict(ols.fit, y), y$ret)
    pred
  } else {
    pred[1, ] <- c(df[1, ]$gvkey, NA, NA)
    pred
  }
}

# Do linear regression and prediction of the return in next quarter.
reg_pred_tech <- function(df) {
  pred <- data.frame(matrix(ncol = 3, nrow = 0))
  names(pred) <- c("permno", "pred", "actual")
  n = nrow(df)
  if (n>31) {
    for(i in c(31:n)){
      x <- df[(i-30):(i-1), ]
      x <- x[complete.cases(x), ]
      y <- df[i, ]
      y <- y[complete.cases(y), ]
      ols.fit <- lm(formula = ret ~ open + close + low + high + vol + sma + ema + mmt + fastK + fastD + slowD + rsi + macd + lwr + adi + cci, data = x)
      if(predict(ols.fit, y) > 0){
        up = 1
      }else{
        up = -1
      }
      pred[nrow(pred) + 1, ] <- c(y$permno, up, y$ret)
  }} else {
      pred[nrow(pred) + 1, ] <- c(df[1,1], NA, NA)
  }
  pred
}

#### Test function.
# df = crsp_cur[crsp_cur$gvkey==1177,]
# reg_pred(df)

# Select out records in certain quarter.
sub_qtr_rec <- function(df, sp500, lkbk, yr, qtr) {
  subset(df, (df$gvkey %in% sp500$gvkey) & (df$date > trans_YQ_to_date(lkbk[1], lkbk[2])) & (df$date <= trans_YQ_to_date(yr, qtr)))
}

# Select out stocks which are included in both feature dataset and return dataset.
get_common_stk <- function(feature, ret) {
  complete_info <- intersect(feature$gvkey, ret$gvkey)
  ret <- subset(ret, (gvkey %in% complete_info))
  feature <- subset(feature, (gvkey %in% complete_info))
  # Now we need to match the number of records.
  complete_info_v1 <- complete_info[table(feature$gvkey) == table(ret$gvkey)]
  ret <- subset(ret, (gvkey %in% complete_info_v1))
  feature <- subset(feature, (gvkey %in% complete_info_v1))
  list(feature, ret)
}

# Given the aim quarter of features, calculate the aim quarter of return.
trans_FQ_to_RQ <- function(fyr, fqtr) {
  test_y_r <- fyr + floor((fqtr + 3) / 5)
  test_q_r <- if (fqtr == 1) 4 else ((fqtr + 3) %% 4)
  c(test_y_r, test_q_r)
}
```

Variable statistics.

```{r}
# Plot the correlation heat map for fundamental factors.
cormat <- round(cor(subset(crsp, select = c(mv, ev, dvy, ebitda2ev, e2pfy0, b2p, s2ev)), use = "complete.obs"), 2)

melted_cormat <- melt(cormat)
jpeg(filename = "Report//Lab//CorHeatMap.jpg")
ggcorrplot(cormat, hc.order = TRUE, type = "upper", lab = TRUE)
dev.off()

crsp_v1 <- subset(crsp, select = c(mv, ev, dvy, ebitda2ev, e2pfy0, b2p, s2ev))
# Now we examine the properties of selected features.
##### NA values in each feature
na_count <- data.frame(sapply(crsp_v1, function(y)
  sum(length(which(is.na(y)))))) / nrow(crsp_v1)
names(na_count) <- c("NA")

# Plot histogram of NA values in column "P/E Ratio" in all the sheet_s elements
jpeg(filename = "Report//Lab//NA_in_factors.jpg", width = 600)
barplot(t(na_count))
dev.off()
```

Main function for fundamental factor stock selection.

```{r}
# Main function:
#   Given a certain quarter for features, this function would return the prediction of stock return in corresponding quarter (2 quarters' later), with lookback period as 20 quarters.
screen_fundamental <- function(test_y_f, test_q_f) {
  test_r <- trans_FQ_to_RQ(test_y_f, test_q_f)

  #### 1. Select out stocks available during certain period.
  lkbk_f <- get_lkbk_period(test_y_f, test_q_f)
  lkbk_r <- get_lkbk_period(test_r[1], test_r[2])
  SP500_list_gvkey <- get_SPlist(trans_YQ_to_date(lkbk_f[1], lkbk_f[2]), trans_YQ_to_date(test_r[1], test_r[2]))

  #### 2. Select out and match the CRSP data and return of stocks from OHLC.
  crsp_cur <- sub_qtr_rec(crsp_f, SP500_list_gvkey, lkbk_f, test_y_f, test_q_f)
  ohlc_cur <- sub_qtr_rec(ohlc, SP500_list_gvkey, lkbk_r, test_r[1], test_r[2])

  #### 3. Then we could merge these two dataframes.
  # Firstly select out available stocks in each dataset.
  fea_ret <- get_common_stk(crsp_cur, ohlc_cur)
  # Sort the records and then add them into one single dataframe.
  ohlc_cur <- fea_ret[[2]][with(fea_ret[[2]], order(gvkey, ym)), ]
  crsp_cur <- fea_ret[[1]][with(fea_ret[[1]], order(gvkey, date)), ]
  crsp_cur$ret <- ohlc_cur$ret

  #### 4. We backtest each stock and predict the performance of next period.

  pred <- crsp_cur %>%
    group_by(gvkey) %>%
    do(reg_pred(.))

  # Now we get the prediction of return in next quarter and actual return.
  # Thus we can evaluate the performance of our model.
  pred
}

#### Test our function.
# test_y_f = 2003
# test_q_f = 3
#
# temp = screen_fundamental(test_y_f,test_q_f)

# evaluate_prediction function.
#   As we could have the prediction and actual returns from our main function, screen_fundamental, we want to examine the performance of our model. Here we would use 2 methods:
#     1. MSE of prediction and actual return.
#     2. Performance of selected stocks according to prediction and the equally weighted benchmark portfolio.
evaluate_prediction <- function(df_) {
  # We do random selection on the stock pool to avoid survivor bias.
  n = as.integer(nrow(df_) * 0.9)
  df = df_[sample(nrow(df_), n), ]
  
  mse <- mean((df$pred - df$actual)^2, na.rm = TRUE)
  r2 <- 1 - mse / mean((df$actual - mean(df$actual, na.rm = TRUE))^2,
    na.rm = TRUE
  )
  temp <- df[complete.cases(df), ]
  temp <- temp[with(temp, order(pred)), ]
  # Equally weighted investment return.
  benchmark <- mean(temp$actual)
  n <- as.integer(nrow(temp) * 0.2)
  mdl <- mean(tail(temp, n)$actual) - mean(head(temp, n)$actual)
  c(mse, r2, benchmark, mdl)
}

# evaluate_prediction function v1.
#   We long the stocks with low expectation and short the stocks with high expectation.
evaluate_prediction_v1 <- function(df_) {
  # We do random selection on the stock pool to avoid survivor bias.
  n = as.integer(nrow(df_) * 0.9)
  df = df_[sample(nrow(df_), n), ]
  
  mse <- mean((df$pred - df$actual)^2, na.rm = TRUE)
  r2 <- 1 - mse / mean((df$actual - mean(df$actual, na.rm = TRUE))^2,
    na.rm = TRUE
  )
  temp <- df[complete.cases(df), ]
  temp <- temp[with(temp, order(pred)), ]
  # Equally weighted investment return.
  benchmark <- mean(temp$actual)
  n <- as.integer(nrow(temp) * 0.2)
  mdl <- -mean(tail(temp, n)$actual) + mean(head(temp, n)$actual)
  c(mse, r2, benchmark, mdl)
}

# Information ratio calculation.
#  We calculate the information ratio given the evaluation of our prediction.
calc_IR <- function(pred){
  attr(pred, "bmk_ir") <- mean(pred$BMK, na.rm = T) / sd(pred$BMK,na.rm = T)
  attr(pred, "mdl_ir") <- mean(pred$MDL, na.rm = T) / sd(pred$MDL,na.rm = T)
  pred
}
```

Check the constitution of S&P 500 in backtest period.

```{r}
# Check if there is 500 stocks in each quarter.
years <- c(1998:2018)
qtrs <- c(1:4)
last_ <- 19980101
stock_num <- data.frame(
  yr = integer(),
  qtr = integer(),
  num = integer()
)

for (y in years) {
  for (q in qtrs) {
    cur_ <- trans_YQ_to_date(y, q)
    const_ <- get_SPlist(last_, cur_)
    stock_num[nrow(stock_num) + 1, ] <- list(y, q, nrow(const_))
    last_ <- cur_
  }
}
jpeg("Report//Lab//Num_of_SP500.jpg")
plot(stock_num$yr + 0.25 * stock_num$qtr, stock_num$num, main = "Number of stocks in SP500", xlab = "Time", ylab = "# of stocks")
```

Rolling screening and evaluate the performance of our linear model.
Fundamental screening, in sample test.

```{r,warning=FALSE}
# Now we could test our model, and store the results.
in_sample <- data.frame(
  yr = integer(), qtr = integer(),
  MSE = numeric(), R2 = numeric(),
  BMK = numeric(), MDL = numeric()
)

in_sample_yrs <- c(2003:2008)
qtrs <- c(1:4)
for (y in in_sample_yrs) {
  for (q in qtrs) {
    pred_yq <- screen_fundamental(y, q)
    res_yq <- evaluate_prediction(pred_yq)
    in_sample[nrow(in_sample) + 1, ] <- c(y, q, res_yq)
  }
}

tiff("Report//Lab//In_sample_qtrly_return.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(in_sample, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = BMK, colour = "BMK")) + 
  geom_line(aes(y = MDL, colour = "MDL")) + 
  labs(x = "Time", y = "Quarterly return") + 
  ggtitle("In sample test from 2003 to 2008") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()

tiff("Report//Lab//In_sample_cumu_return.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(in_sample, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = cumsum(BMK), colour = "BMK")) + 
  geom_line(aes(y = cumsum(MDL), colour = "MDL")) + 
  labs(x = "Time", y = "Cumulative return") + 
  ggtitle("In sample test from 2003 to 2008") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()

tiff("Report//Lab//In_sample_r2.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(in_sample, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = R2, colour = "R2")) + 
  labs(x = "Time", y = "Quarterly R2") + 
  ggtitle("In sample test from 2003 to 2008") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()
```

Re-test the in sample period.

```{r,warning=FALSE}
in_sample_v1 <- data.frame(
  yr = integer(), qtr = integer(),
  MSE = numeric(), R2 = numeric(),
  BMK = numeric(), MDL = numeric()
)

for (y in in_sample_yrs) {
  for (q in qtrs) {
    pred_yq <- screen_fundamental(y, q)
    res_yq <- evaluate_prediction_v1(pred_yq)
    in_sample_v1[nrow(in_sample_v1) + 1, ] <- c(y, q, res_yq)
  }
}

in_sample_v1 <- calc_IR(in_sample_v1)

tiff("Report//Lab//In_sample_qtrly_return_v1.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(in_sample_v1, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = BMK, colour = "BMK")) + 
  geom_line(aes(y = MDL, colour = "MDL")) + 
  labs(x = "Time", y = "Quarterly return") + 
  ggtitle("In sample test from 2003 to 2008") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()

tiff("Report//Lab//In_sample_cumu_return_v1.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(in_sample_v1, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = cumsum(BMK), colour = "BMK")) + 
  geom_line(aes(y = cumsum(MDL), colour = "MDL")) + 
  labs(x = "Time", y = "Cumulative return") + 
  ggtitle("In sample test from 2003 to 2008") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()
```

Now we test our model in out of sample period.

```{r,warning=FALSE}

# Now we could test our model, and store the results.
out_sample <- data.frame(
  yr = integer(), qtr = integer(),
  MSE = numeric(), R2 = numeric(),
  BMK = numeric(), MDL = numeric()
)

out_sample_yrs <- c(2009:2018)
qtrs <- c(1:4)
for (y in out_sample_yrs) {
  for (q in qtrs) {
    pred_yq <- screen_fundamental(y, q)
    res_yq <- evaluate_prediction_v1(pred_yq)
    out_sample[nrow(out_sample) + 1, ] <- c(y, q, res_yq)
  }
}

out_sample <-  calc_IR(out_sample)

tiff("Report//Lab//Out_sample_qtrly_return.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(out_sample, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = BMK, colour = "BMK")) + 
  geom_line(aes(y = MDL, colour = "MDL")) + 
  labs(x = "Time", y = "Quarterly return") + 
  ggtitle("Out sample test from 2009 to 2018") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()

tiff("Report//Lab//Out_sample_cumu_return.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(out_sample, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = cumsum(BMK), colour = "BMK")) + 
  geom_line(aes(y = cumsum(MDL), colour = "MDL")) + 
  labs(x = "Time", y = "Cumulative return") + 
  ggtitle("Out sample test from 2009 to 2018") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()

tiff("Report//Lab//Out_sample_r2.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(out_sample, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = R2, colour = "R2")) + 
  labs(x = "Time", y = "Quarterly R2") + 
  ggtitle("Out sample test from 2009 to 2018") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()
```

```{r}
attr(in_sample_v1,"bmk_ir")
attr(in_sample_v1,"mdl_ir")
attr(out_sample,"bmk_ir")
attr(out_sample,"mdl_ir")
```

Verification part.

Part1 : Late efficiency.
```{r,warning=FALSE}
# use most recent quarter as dependent variable

trans_FQ_to_RQ_v1 <- function(fyr, fqtr) {
  test_y_r <- fyr + floor((fqtr + 1) / 5)
  test_q_r <- if (fqtr == 4) 1 else (fqtr + 1)
  c(test_y_r, test_q_r)
}

screen_fundamental_v1 <- function(test_y_f, test_q_f) {
  test_r <- trans_FQ_to_RQ_v1(test_y_f, test_q_f)

  #### 1. Select out stocks available during certain period.
  lkbk_f <- get_lkbk_period(test_y_f, test_q_f)
  lkbk_r <- get_lkbk_period(test_r[1], test_r[2])
  SP500_list_gvkey <- get_SPlist(trans_YQ_to_date(lkbk_f[1], lkbk_f[2]), trans_YQ_to_date(test_r[1], test_r[2]))

  #### 2. Select out and match the CRSP data and return of stocks from OHLC.
  crsp_cur <- sub_qtr_rec(crsp_f, SP500_list_gvkey, lkbk_f, test_y_f, test_q_f)
  ohlc_cur <- sub_qtr_rec(ohlc, SP500_list_gvkey, lkbk_r, test_r[1], test_r[2])

  #### 3. Then we could merge these two dataframes.
  # Firstly select out available stocks in each dataset.
  fea_ret <- get_common_stk(crsp_cur, ohlc_cur)
  # Sort the records and then add them into one single dataframe.
  ohlc_cur <- fea_ret[[2]][with(fea_ret[[2]], order(gvkey, ym)), ]
  crsp_cur <- fea_ret[[1]][with(fea_ret[[1]], order(gvkey, date)), ]
  crsp_cur$ret <- ohlc_cur$ret

  #### 4. We backtest each stock and predict the performance of next period.

  pred <- crsp_cur %>%
    group_by(gvkey) %>%
    do(reg_pred(.))

  # Now we get the prediction of return in next quarter and actual return.
  # Thus we can evaluate the performance of our model.
  pred
}

# Now we could test our model, and store the results.
out_sample_v1 <- data.frame(
  yr = integer(), qtr = integer(),
  MSE = numeric(), R2 = numeric(),
  BMK = numeric(), MDL = numeric()
)

out_sample_yrs <- c(2009:2018)
qtrs <- c(1:4)
for (y in out_sample_yrs) {
  for (q in qtrs) {
    pred_yq <- screen_fundamental_v1(y, q)
    res_yq <- evaluate_prediction(pred_yq)
    out_sample_v1[nrow(out_sample_v1) + 1, ] <- c(y, q, res_yq)
  }
}

out_sample_v1 <-  calc_IR(out_sample_v1)

tiff("Report//Lab//Out_sample_qtrly_return_v1.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(out_sample_v1, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = BMK, colour = "BMK")) + 
  geom_line(aes(y = MDL, colour = "MDL")) + 
  labs(x = "Time", y = "Quarterly return") + 
  ggtitle("Out sample test from 2009 to 2018") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()

tiff("Report//Lab//Out_sample_cumu_return_v1.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(out_sample_v1, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = cumsum(BMK), colour = "BMK")) + 
  geom_line(aes(y = cumsum(MDL), colour = "MDL")) + 
  labs(x = "Time", y = "Cumulative return") + 
  ggtitle("Out sample test from 2009 to 2018") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()

tiff("Report//Lab//Out_sample_r2_v1.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(out_sample_v1, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = R2, colour = "R2")) + 
  labs(x = "Time", y = "Quarterly R2") + 
  ggtitle("Out sample test from 2009 to 2018") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()

attr(out_sample_v1,"bmk_ir")
attr(out_sample_v1,"mdl_ir")
```

Part2 : Mean reverting test.
```{r}
# ADF Test
# main type 3, count the efficient p-value in each lag.

ADF_results <- data.frame(
  gvkey = integer(), lag_0 = integer(),
  lag_1 = numeric(), lag_2 = numeric(),
  lag_3 = numeric()
)

record_ADF <- function(df_1,df_2){
  # df_1 : data.frame to store ADF results
  # df_2 : data.frame which stores returns of stocks.
  
  stks = unique(df_2$gvkey)
  
  for(k in stks){
    print(k)
    temp <- df_2[df_2$gvkey == k,]
    if(nrow(temp)>20){
      res <- adf.test(temp$ret)[[3]][,3]
      if(length(res)<4){
        res[(length(res)+1):4] = NA
      }
      df_1[nrow(df_1) + 1, ] <- c(k,res) 
    }
  } 
  df_1
}

ADF_results <- record_ADF(ADF_results,ohlc)

# We count the number of stocks which has p-value less than 0.05.
mean_rev_num = c()
for(i in c(1:4)){
  mean_rev_num = append(mean_rev_num,sum(ADF_results[,i+1] < 0.05, na.rm = T))
}

# We transform the number of stocks into percentage to make it comparable.
mean_rev_num = mean_rev_num/nrow(ADF_results)

# Plot the percentage.
tiff("Report//Lab//mean_rev_pctg.jpg", units="in", width = 6, height = 4, res = 125)
barplot(mean_rev_num, names.arg = c("lag0","lag1","lag2","lag3"), border="black", 
        xlab = "Lag",ylab = "Percentage",
        main = "Percentage of stocks proved mean reversion",ylim = c(0,1))
abline(h = 0.8,col = "red",lty = 2, lwd = 2)
dev.off()
```

Part3 : Bull market statistics.
```{r}
# 2009-2018 count positive return stocks number
count_stk_num <- function(df){
  data.frame(nrow(df),nrow(df[df$ret > 0,]))
}

out_sample_ohlc = ohlc[ohlc$ym > 200900,]

pos_stk_num <- out_sample_ohlc %>%
    group_by(ym) %>%
    do(count_stk_num(.))
names(pos_stk_num) = c("Quarter","Total","Pos")

pos_stk_num$Percentage = pos_stk_num$Pos/pos_stk_num$Total

tiff("Report//Lab//Pos_stock_ptg.jpg", units="in", width = 6, height = 4, res = 125)
barplot(pos_stk_num$Percentage, names.arg = pos_stk_num$Quarter, border="black", 
        xlab = "Quarter",ylab = "Percentage",
        main = "Percentage of stocks with positive return",ylim = c(0,1))
dev.off()

# Plot the distribution of percentages.
tiff("Report//Lab//Pos_stock_ptg_dist.jpg", units="in", width = 6, height = 4, res = 125)
barplot(pos_stk_num[order(pos_stk_num$Percentage),]$Percentage, border="black", 
        xlab = "Distribution",ylab = "Percentage",
        main = "Percentage of stocks with positive return",ylim = c(0,1))
abline(h = 0.5,col = "red",lty = 2, lwd = 2)
dev.off()

```

Main function for fundamental factor technical stock trading.

```{r}

tech_trading <- function(df, yr, qtr, stk_list){

  #### 1. Select out stocks available during certain period.
  lkbk <- get_lkbk_period_tech(yr, qtr)
  stk_list <- intersect(stk_list,unique(df$permno))
  
  tech_factors_cur <- subset(df, (df$permno %in% stk_list) 
                             & (df$date > trans_YQ_to_date(lkbk[1], lkbk[2]))
                             & (df$date <= trans_YQ_to_date(yr, qtr)))
  
  #### 2. Now we get the prediction of return in next quarter and actual return.
  pred <- tech_factors_cur %>%
    group_by(permno) %>%
    do(reg_pred_tech(.))

  # Now we get the prediction of return in next quarter and actual return.
  # Thus we can evaluate the performance of our model.
  pred
}

evaluate_prediction_tech <- function(df, yr, qtr, pred){
  pred$mdl <- pred$pred*pred$actual
  total_mdl <- pred %>%
    group_by(permno) %>%
    summarise(mdl = sum(mdl))
  
  total_bmk <- pred %>%
    group_by(permno) %>%
    summarise(bmk = sum(actual))
  
  total_mdl$bmk = total_bmk$bmk
  
  total_mdl$yr = yr
  total_mdl$qtr = qtr
  
  total_mdl = total_mdl[,c('yr','qtr','permno','mdl','bmk')]
  
  total_mdl
}

# Construct portfolios according to fundamental screening.
fundamental_to_tech <- function(tech_full, yr, qtr, fund_pred){
  fund_pred <- fund_pred[with(fund_pred, order(pred)), ]
  n <- as.integer(nrow(fund_pred) * 0.2)
  long_list <- subset(link_key,(link_key$GVKEY %in% tail(fund_pred, n)$gvkey))
  short_list <- subset(link_key,(link_key$GVKEY %in% head(fund_pred,n)$gvkey))
  
  long_pool <- subset(tech_full, (tech_full$permno %in% long_list$PERMNO) 
                             & (tech_full$yr == yr)
                             & (tech_full$qtr == qtr))
  short_pool <- subset(tech_full, (tech_full$permno %in% short_list$PERMNO) 
                             & (tech_full$yr == yr)
                             & (tech_full$qtr == qtr))
  mdl <- (mean(long_pool$mdl) - mean(short_pool$mdl))
  bmk <- (mean(long_pool$bmk) - mean(short_pool$bmk))
  c(yr, qtr, mdl,bmk)
}

```

We test all available stocks' performance in test period and store them in an excel.

```{r}

out_sample_yrs <- c(2009:2018)
qtrs <- c(1:4)

res_tech <- data.frame(
  yr = integer(), qtr = integer(),
  permno = integer(), mdl = double(),
  bmk = double()
)

for (y in out_sample_yrs) {
  for (q in qtrs) {
    pred <- tech_trading(tech_factors,2009,1,unique(tech_factors$permno))
    evaluation <- evaluate_prediction_tech(res_tech, y, q, pred)
    res_tech[(nrow(res_tech)+1):(nrow(res_tech)+nrow(evaluation)),] = evaluation
  }
}

# We save the results thus we don't need to recalculate it everytime.
writexl::write_xlsx(res_tech, path = "D:\\data\\Capstone\\Data\\Tech_test.xlsx", col_names = TRUE)
```

Combine fundamental and technical methods.

```{r}
res_tech <- readxl::read_xlsx("D:\\data\\Capstone\\Data\\Tech_test.xlsx")

out_sample_yrs <- c(2009:2018)
qtrs <- c(1:4)

out_sample_v2 <- data.frame(
  yr = integer(), qtr = integer(),
  mdl = double(), bmk = double()
)

for (y in out_sample_yrs) {
  for (q in qtrs) {
    pred_yq <- screen_fundamental(y, q)
    out_sample_v2[nrow(out_sample_v2) + 1, ] <- fundamental_to_tech(res_tech, y, q, pred_yq)
  }
} 

# Plot the quarterly and cumulative return.
tiff("Report//Lab//full_model.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(out_sample_v2, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = bmk, colour = "BMK")) + 
  geom_line(aes(y = mdl, colour = "MDL")) + 
  labs(x = "Time", y = "Quarterly return") + 
  ggtitle("Out sample test from 2009 to 2018") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()

tiff("Report//Lab//full_model_cumu.jpg", units="in", width = 6, height = 4, res = 125)
ggplot(out_sample_v2, aes(yr+0.25*qtr)) + 
  geom_line(aes(y = cumsum(bmk), colour = "BMK")) + 
  geom_line(aes(y = cumsum(mdl), colour = "MDL")) + 
  labs(x = "Time", y = "Quarterly return") + 
  ggtitle("Out sample test from 2009 to 2018") +
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white",color = "black")) + 
  scale_x_continuous(breaks= pretty_breaks())
dev.off()
```

